On the Evolution of Choice Principles

### 2014-08-06 text/RoaM_proceedings/paper.tex
grant info added

\title{On the Evolution of Choice Principles}
\titlerunning{On the Evolution of Choice Principles}
\author{Michael Franke\inst{1} \and Paolo Galeazzi \inst{2}}
\institute{Department of Linguistics, University of T\"{u}bingen \and
  Institute for Logic, Language and Computation, Universiteit van Amsterdam}
\date{}

>>>>

\title{On the Evolution of Choice Principles} \titlerunning{On the
  Evolution of Choice Principles} \author{Michael Franke\inst{1} \and
  Paolo Galeazzi \inst{2}\thanks{ Michael Franke gratefully
    acknowledges support by NWO-VENI-grant 275-80-004. The research of
    Paolo Galeazzi leading to these results has received funding from
    the European Research Council under the European Community's
    Seventh Framework Programme (FP7/2007-2013)/ERC Grant agreement
    no. 283963.}}  \institute{Department of Linguistics, University of
  T\"{u}bingen \and Institute for Logic, Language and Computation,
  Universiteit van Amsterdam} \date{}
